A young star cluster in the Galactic halo: \\ Recent star formation associated with the Leading Arm of the Magellanic stream

### 2018-05-21 ms.tex
Title
Update on Overleaf.

\title{A young cluster in the Galactic halo: \\
Recent star formation associated with the Magellanic stream}

@@

The stellar halo of the Milky Way is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the Milky Way's formation: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
These systems likely came in with significant gas reservoirs, but were quenched and stripped of their gas, leading to the typically old stellar halo population in place today.
(Gas stripped now too hot/diffuse to form stars)

However, the Milky Way continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy (cite), and the presence of the Large and Small Magellanic Clouds (LMC, SMC).
While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC--SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky (cite nidever).
By modeling the LMC--SMC interaction and infall, ... sims to reproduce gas velocity vs. longitude \citep{Besla:2010}
(But lacks distance constraints)
(Many people search for stars associated with the stream, but must be diffuse)

@@

Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at
a distance of 25 kpc.  Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever2008}.
The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
position of the cluster.

@@

We have used the new Gaia data to detect a young, metal-poor cluster in the halo of the Milky Way at a distance of 25 kpc and
a Milky Way z-height of 12 kpc.  The detection of such a young cluster so far from the star-forming disks of any nearby
galaxy is highly unusual.  However, the proximity of the new cluster to the Leading Arm of the Magellanic Stream suggests
that the cluster originated from this metal-poor gas \citep{Fox2018}.  Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu2014,MoniBidin2017}, however, this is the first time
that an entire star cluster has been detected so far from the Clouds.

>>>>

\title{A young star cluster in the Galactic halo: \\
Recent star formation associated with the Leading Arm of the Magellanic stream}

@@

The stellar halo of the Milky Way (MW) is characterized by its old ($\approx XX$--$YY~\textrm{Gyr}$), metal-poor ($\feh \approx -1.5$) stellar population.
This is understood as a signature of the dominant (in stellar mass) progenitor systems that were accreted and disrupted early on in the MW's formation: massive dwarf galaxies \citep[e.g.,][]{Deason:2015, Fiorentino:2015}.
These systems likely came in with significant gas reservoirs, but were quenched and stripped of their gas, leading to the typically old stellar halo population in place today.
(Gas stripped now too hot/diffuse to form stars)

However, the MW continues to accrete satellite galaxies, as is evidenced by the prominent stellar stream from the Sagittarius dwarf galaxy (cite), and the presence of the Large and Small Magellanic Clouds (LMC, SMC).
While Sagittarius was likely stripped of its neutral gas long ago (cite), the LMC--SMC system contains $\approx XX~\msun$ of HI gas (cite), which form leading and trailing gas streams that cover $\approx 200^\circ$ on the sky (cite nidever).
By modeling the LMC--SMC interaction and infall, ... sims to reproduce gas velocity vs. longitude \citep{Besla:2010}
(But lacks distance constraints)
(Many people search for stars associated with the stream, but must be diffuse)

@@

Figure \ref{fig_skypm} shows the spatial and proper motion distribution in the region of interest with the objects in
a small proper motion selection shown as black and red dots.  The color magnitude diagram (CMD) of the same objects
is shown in Figure \ref{fig_cmd} and clearly reveals a sequence of objects that follow the shape of a young main-sequence.
The PS1 photometry of the same region is shown in Figure \ref{fig_isochrone} and as well as young, metal-poor isochrones at fa distance of 25 kpc.  Finally, Figure \ref{fig_gass} shows a position-velocity diagram at the position of the cluster of the \citep[GASS;][]{McClure-Griffiths2009} \hi data that has been Gaussian decomposed using the technique in \citet{Nidever2008}.
The component of the LA II can be seen on the left-hand side of the figure and a similar \hie stream can be seen near the
position of the cluster.
% Yumi:
% Need a sentence or two for dust extinction correction somewhere in the above two paragraphs?

@@

We have used the new Gaia data to detect a young, metal-poor cluster in the halo of the Milky Way at a distance of 25 kpc and a MW z-height of 12 kpc.  The detection of such a young cluster so far from the star-forming disks of any nearby
galaxy is highly unusual.  However, the proximity of the new cluster to the Leading Arm of the Magellanic Stream suggests
that the cluster originated from this metal-poor gas \citep{Fox2018}.  Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu2014,MoniBidin2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.
